\documentclass[12pt,a4paper,twoside,openright]{report}

%%%%%%% Import packages %%%%%%%
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{epstopdf,amsfonts,array,multirow,amsmath,tabularx,setspace,amssymb,enumerate,csquotes}
	
% \usepackage{url}
% \usepackage{bbm}
% \usepackage{eufrak}
% \usepackage{marvosym}
% \usepackage{moderncvcompatibility}

%% packages with settings
% Inline listing package
% \usepackage[inline]{enumitem}
\usepackage{listings}
% Page geometry
\usepackage{geometry}
\setlength{\evensidemargin}{0.0cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\topmargin}{-1.27cm}
\setlength{\headheight}{32pt}
\setlength{\headsep}{1em} %% Setting for gap in header and main body%%
\setlength{\textheight}{24.0cm}
%\setlength{\textwidth}{14.65cm}
\setlength{\footskip}{1.5cm}
\setlength{\parindent}{1.5em}
\setlength{\parskip}{1em}

% Set line spacing to 1.25 because
% with 12pt font, 1.5 spacing is too large
\setstretch{1.25}

\usepackage{fancyhdr}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{relsize}
\usepackage{bigints}

% Packages for table of contents
\setcounter{tocdepth}{3}

\usepackage[nottoc]{tocbibind}
\usepackage[titles,subfigure]{tocloft}

\makeatletter
\newlength{\@chapterlength} % Original Magic Value - RMR
\setlength{\@chapterlength}{1.5em} % This code adds space for \@chapapp for toc entries
\newcommand\@chapterheadsmark{1}
\ifnum \@chapterheadsmark = 1
\settowidth{\@chapterlength}{\@chapapp}
\addtolength{\@chapterlength}{3.8em} % Space between toc labels and values
\fi
% \def\l@chapter{\pagebreak[3]\vskip 1em plus 1pt \@dottedtocline{0}{0em}{1.5em}}
% \def\l@chapter{\pagebreak[3]\vskip 1em plus 1pt \@dottedtocline{0}{0em}{\@chapterlength}}

\def\l@section{\@dottedtocline{1}{\@chapterlength}{2.3em}}

\newlength{\@subsectionlength}
\setlength{\@subsectionlength}{\@chapterlength}
\addtolength{\@subsectionlength}{2.3em}
\def\l@subsection{\@dottedtocline{2}{\@subsectionlength}{3.2em}}

\newlength{\@subsubsectionlength}
\setlength{\@subsubsectionlength}{\@chapterlength}
\addtolength{\@subsubsectionlength}{5.5em}
\def\l@subsubsection{\@dottedtocline{3}{\@subsubsectionlength}{4.1em}}

\newlength{\@paragraphlength}
\setlength{\@paragraphlength}{\@chapterlength}
\addtolength{\@paragraphlength}{8.5em}
\def\l@paragraph{\@dottedtocline{4}{\@paragraphlength}{5em}}

\newlength{\@subparagraphlength}
\setlength{\@subparagraphlength}{\@chapterlength}
\addtolength{\@subparagraphlength}{10.5em}
\def\l@subparagraph{\@dottedtocline{5}{\@subparagraph}{6em}}
\makeatother

\renewcommand\cftchappresnum{\chaptername~}
\newlength\mylength
\settowidth\mylength{\cftchappresnum\cftchapaftersnum\qquad}
\addtolength\cftchapnumwidth{\mylength}

\usepackage[acronym,nomain,toc]{glossaries}
\makeglossaries
\usepackage[intoc]{nomencl}
\makenomenclature
\renewcommand{\nomname}{List of Symbols}
\usepackage[toc,page]{appendix}

% Packages for floats like figures and tables
\usepackage{float}
\usepackage{caption}
% \usepackage[center]{caption}
% \usepackage{longtable}
% \usepackage{subfig}
\usepackage{subfigure}
% \usepackage{subcaption}
% \usepackage[chapter]{algorithm}
\usepackage{algpseudocode}
% \usepackage{algorithmic}

\usepackage[base]{babel}
\usepackage{lipsum,blindtext} % just to generate text for the example

\usepackage{color}   %May be necessary if you want to color links

\usepackage{datetime}
\newdateformat{thisdate}{%
	\twodigit{\THEDAY}}
\newdateformat{thismonthdigit}{%
	\twodigit{\THEMONTH}}
\newdateformat{thismonth}{%
	\monthname[\THEMONTH]}
\newdateformat{thisyear}{%
	\THEYEAR}

% \usepackage{cite}
% \usepackage{notoccite}
\usepackage[backend=biber, style=ieee, sorting=none, defernumbers=true]{biblatex}
\addbibresource{bibliography.bib}

% Hyperref should be the last package to be loaded
\usepackage{hyperref}
% \hypersetup{
% 	breaklinks=true,
%     colorlinks=true, %set true if you want colored links
%     linktoc=all,     %set to all if you want both sections and subsections linked
%     linkcolor=black,  %choose some color if you want links to stand out
%     citecolor=black,
%     urlcolor=black
% }

\hypersetup{linktoc=all, colorlinks=true, linkcolor=Black, citecolor=teal, urlcolor=red}


\DeclareMathOperator{\arccot}{arccot}
\DeclareMathOperator{\sinc}{sinc}
\DeclareMathOperator*{\argmin}{arg\;min}
\DeclareMathOperator*{\argmax}{arg\;max}

\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{definition}{Definition}[chapter]
\newtheorem{prop}{Proposition}
%-------------------------------------------------------------------

%\flushbottom
%--------------------------------------------------------------------------
\raggedbottom                               % (Remove Unnecessary space b/w paragraphs)
%--------------------------------------------------------------------------
\begin{document}

% --------- Title and abstract etc in the front matter ----------- %
\pagenumbering{gobble}
\input{00_Cover/cover_page}

%%%%%%%%%%%% Front Matter %%%%%%%%%%%%
\pagenumbering{roman}
\include{01_Declaration/Declaration}
\include{02_Approval/Approval}
 
%%%%%%%%%%%% Abstract %%%%%%%%%%%%
\setstretch{2}  % double spacing
\input{06_Abstract/Abstract}


%%%%%% Table of Contents %%%%%%
%%%%%%% To create 1.5 spacing in contents
\setstretch{1.5}

\input{09_Contents/Contents}

\pagenumbering{arabic}
%%%%%%%% To create double spacing in chapters
\setstretch{2}

% Fancy header
\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{\thesection~#1}{}}
\renewcommand{\chaptermark}[1]{\markboth{\chaptername~\thechapter~-~#1}{}}
\fancyhf{}
%\fancyhead[RE]{\leftmark}
%\fancyhead[LO]{\rightmark}
\fancyhead[LE,RO]{\thepage}

%%%%%% Chapters %%%%%%
%% Remove any command starting with "\lipsum"
%% from the chapter text. They are used to generate
%% junk test paragraphs

\input{10_Chapter_1/Introduction}
\newpage
%\newpage\null\newpage
\input{20_Chapter_2/Literature_review}
\newpage
%\newpage\null\newpage
\input{30_Chapter_3/chapter_3}
\newpage
%\newpage\null\newpage
\input{40_Chapter_4/chapter_4}
\newpage
%\newpage\null\newpage
\input{50_Chapter_5/chapter_5}
\newpage
\input{70_Deployment/Deploymnet}
\newpage
%\newpage\null\newpage
\input{60_Conclusion/Conclusion}
\newpage

%%%%%% Appendices %%%%%%
\appendix
\renewcommand{\chaptername}{Appendix}
\addtocontents{toc}{\protect\renewcommand{\protect\cftchappresnum}{\chaptername~}}
\input{100_Appendices/appendix_0}
\newpage
% \null\newpage

\setstretch{1}

\vspace{12pt}
\begin{thebibliography}{00}
\bibitem{b1} Bourne, R. R., Stevens, G. A., White, R. A., Smith, J. L., Flaxman, S. R., Price, H., Jonas, J. B., Keeffe, J., Leasher, J., Naidoo, K., Pesudovs, K., Resnikoff, S., & Taylor, H. R. (2013). Causes of vision loss worldwide, 1990–2010: a systematic analysis. The Lancet Global Health, 1(6). https://doi.org/10.1016/s2214-109x(13)70113-x 
\bibitem{b2} Sommer, A., Tielsch, J. M., Katz, J., Quigley, H. A., Gottsch, J. D., Javitt, J. C., Martone, J. F., Royall, R. M., Witt, K. A., & Ezrine, S. (1991). Racial Differences in the Cause-Specific Prevalence of Blindness in East Baltimore. New England Journal of Medicine, 325(20), 1412–1417. https://doi.org/10.1056/nejm199111143252004 
\bibitem{b3} Congdon, N., O'Colmain, B., Klaver, C. C., Klein, R., Muñoz, B., Friedman, D. S., Kempen, J., Taylor, H. R., Mitchell, P., & Eye Diseases Prevalence Research Group (2004). Causes and prevalence of visual impairment among adults in the United States. Archives of ophthalmology (Chicago, Ill. : 1960), 122(4), 477–485. 
\bibitem{b4} Application of Ocular Fundus Photography and Angiography. (2014). Ophthalmological Imaging and Applications, 154–175. https://doi.org/10.1201/b17026-12 
\bibitem{b5} Rowe, S., MacLean, C. H., & Shekelle, P. G. (2004). Preventing Visual Loss From Chronic Eye Disease in Primary Care. JAMA, 291(12), 1487. https://doi.org/10.1001/jama.291.12.1487 
\bibitem{b6} Kessel, L., Erngaard, D., Flesner, P., Andresen, J., Tendal, B., & Hjortdal, J. (2015). Cataract surgery and age‐related macular degeneration. An evidence‐based update. Acta Ophthalmologica, 93(7), 593–600. https://doi.org/10.1111/aos.12665Li, N., Li, T., Hu, C., Wang, K.
\bibitem{b7} Li, N., Li, T., Hu, C., Wang, K., & Kang, H. (2021). A Benchmark of Ocular Disease Intelligent Recognition: One Shot for Multi-disease Detection. Benchmarking, Measuring, and Optimizing, 177–193. https://doi.org/10.1007/978-3-030-71058-3-11
\bibitem{b8}K. N. Alam, M. S. Khan, A. R. Dhruba et al., “Deep learning-based sentiment analysis of COVID-19 vaccination responses from Twitter data,” Computational and Mathematical Methods in Medicine, vol. 2021, pp. 1–15, 2021.
\bibitem{b9}J. He, C. Li, J. Ye, Y. Qiao, and L. Gu, “Self-speculation of clinical features based on knowledge distillation for accurate ocular disease classification,” Biomedical Signal Processing and Control, vol. 67, Article ID 102491, 2021.
\bibitem{b10}K. N. Alam and M. M. Khan, “CNN based COVID-19 prediction from chest X-ray images,” in Proceedings of the 2021 IEEE 12th Annual Ubiquitous Computing, Electronics & Mobile Communication Conference (UEMCON), pp. 0486–0492, IEEE, New York, USA, 1 December 2021.
\bibitem{b11}A. G. Roy, S. Conjeti, S. P. K. Karri et al., “ReLayNet: retinal layer and fluid segmentation of macular optical coherence tomography using fully convolutional networks,” Biomedical Optics Express, vol. 8, no. 8, pp. 3627–3642, 2017.
\bibitem{b12}C. S. Lee, A. J. Tyring, N. P. Deruyter, Y. Wu, A. Rokem, and A. Y. Lee, “Deep-learning based, automated segmentation of macular edema in optical coherence tomography,” Biomedical Optics Express, vol. 8, no. 7, pp. 3440–3448, 2017.
\bibitem{b13}S. P. K. Karri, D. Chakraborty, and J. Chatterjee, “Transfer learning based classification of optical coherence tomography images with diabetic macular edema and dry age-related macular degeneration,” Biomedical Optics Express, vol. 8, no. 2, pp. 579–592, 2017.
\bibitem{b14}M. Oda, T. Yamaguchi, H. Fukuoka, Y. Ueno, and K. Mori, “Automated Eye Disease Classification Method from Anterior Eye Image Using Anatomical Structure Focused Image Classification Technique,” 2020, https://arxiv.org/abs/2005.01433.
\bibitem{b15}F. Eperjesi, C. W. Fowler, and A. J. Kempster, “Luminance and chromatic contrast effects on reading and object recognition in low vision: a review of the literature,” Ophthalmic and Physiological Optics, vol. 15, no. 6, pp. 561–568, 1995.
\bibitem{b16}N. M. Dipu, S. Alam Shohan, and K. M. A. Salam, “Ocular disease detection using advanced neural network based classification algorithms,” ASIAN JOURNAL OF CONVERGENCE IN TECHNOLOGY, vol. 7, no. 2, pp. 91–99, 2021.
\bibitem{b17}M. S. Khan et al., “Deep learning for ocular disease recognition: An inner-class balance,” Comput. Intell. Neurosci., vol. 2022, p. 5007111, 2022.
\bibitem{b18} L. Jain, H. V. S. Murthy, C. Patel and D. Bansal, "Retinal Eye Disease Detection Using Deep Learning," 2018 Fourteenth International Conference on Information Processing (ICINPRO), 2018, pp. 1-6, doi: 10.1109/ICINPRO43533.2018.9096838.
\bibitem{b19} Nazir, T.; Irtaza, A.; Javed, A.; Malik, H.; Hussain, D.; Naqvi, R.A. Retinal Image Analysis for Diabetes-Based Eye Disease Detection Using Deep Learning. Appl. Sci. 2020, 10, 6185. https://doi.org/10.3390/app10186185
\bibitem{b20}Sarki, R., Ahmed, K., Wang, H. et al. Automated detection of mild and multi-class diabetic eye diseases using deep learning. Health Inf Sci Syst 8, 32 (2020). https://doi.org/10.1007/s13755-020-00125-5
\bibitem{b21} J. Shan and L. Li, "A Deep Learning Method for Microaneurysm Detection in Fundus Images," 2016 IEEE First International Conference on Connected Health: Applications, Systems and Engineering Technologies (CHASE), 2016, pp. 357-358, doi: 10.1109/CHASE.2016.12.
\bibitem{b22} Malik, S.; Kanwal, N.; Asghar, M.N.; Sadiq, M.A.A.; Karamat, I.; Fleury, M. Data Driven Approach for Eye Disease Classification with Machine Learning. Appl. Sci. 2019, 9, 2789. https://doi.org/10.3390/app9142789
\bibitem{b23} “Ocular disease recognition,” https://www.kaggle.com/andrewmvd/ocular-disease-recognition-odir5k.
\end{thebibliography}
\vspace{12pt}
\end{document}
